\chapter{Acknowledgements}
\label{acknowledgements_overview}

\par First and foremost, the analysis described in this dissertation
would be impossible without the thousands of individuals that have
contributed to the design, construction, and commissioning of the
Large Hadron Collider (LHC) and Compact Muon Solendoid (CMS)
experiment.  The countless years of passion and dedication that have
been poured into these machines have resulted in the most
sophisticated tools ever available to mankind to explore the frontiers
of high energy physics.  I am extremely grateful for the opportunity
to participate in this collaboration and to contribute to the
undertanding of physics at the \TeV energy scale.  

\par I would like to thank Mike Arenton, Dave Cockerill and Alexander
Ledovskoy for their tutelage and mentorship in regards to my studies
with the UVa Vacuum Photo-Triode (VPT) rig.  This project has been a
critical to improving my understanding of electronics, firmware, and
signal analysis, and has been both a challenging and exciting
experience.  I would also like to thank Thomas Anderson, Brian
Franchise, Joseph Goodell, Al Tobias, and Evan Wolfe for all of their help in
maintiaining the 4 T magnet and ensuring the VPT rig has survived long
enough to collect and analyze the data on these devices.  I woud also
like to thank Professors Brad Cox and Bob Hirosky of the CMS research
group here at UVa for always challenging me to improve the VPT rig and
analysis, while still providing me with all of the tools and input I
needed to succeed.   

\par The \ttH analysis group at CMS has been provided an incredibly
supportive environment to learn about particle physics and data
analysis.  I would like to thank Professor Kevin Lannon of the
University of Notre Dame (ND) and Professors Richard Hughes and Brian
Winer of the Ohio State University (OSU) for pushing the group as hard
as possible while still maintaining a high level of quality for the
work and studies presented each week. Additional thanks go out to the
post-doctoral and graduate students at these Universities: Darren
Puigh and Geoff Smith of ND and Jason Slaunwhite, Andrew Brinkerhoff,
Wuming Luo, and Anna Woodard of OSU, without whom, this analysis would
not have been published twice, nor would I be reflecting so fondly on
a period of times that involved an intense set of deadlines and a lot
of late nights.  

\par To my fellow graduate students and good friends here at UVa:
Thomas Anderson, Tanwa Apornthip, Alexandr Arakelyan, Sana Deshmukh,
Ryan Duve, Adam Fallon, Brian Francis, Joe Johnson, Manolis
Kargiantoulakis, Micah Shiable, Julie Spencer, Niranjan Sridhar, Evan
Wolfe, and too many more to list, you know who you are, thank you for
so many wonderfully hazy nights that have helped me from going insane
in graduate school. To my friends abroad: Supaksh Gupta, Kat Hunter,
Ryan Karlsgodt, Kevin Karlsgodt, Ginny Morris, Mark Nicholson, Matt
Pierce, Mikey Sheffield, Tyler Vickers, and the many others who also
know who you are, thank you for continuing to be amazing friends
throughout all these years apart.  

\par  I would like to give special thanks to Dr. Sarah Boutle, who has
been an amazing mentor and friend.   I owe so much of my understanding
of particle physics, the LHC, and CMS to the countless conversations
and coffee breaks we shared.  I have been incredibly lucky to also
have a role model of someone who has balanced a successful career as
a scientist and still manages to maintain a caring, well-grounded
personality with a great sense of humor, even during the most daunting
and stressful of situations.    

\par These ackowledgements would be incomplete without mention of
Professor Chris Neu, who hooked me on studying particle physics at CMS
during our first conversation together.  Since then, I have had the
priviledge of being his student for the past six years.  It has been
an incredibly rewarding experience.  Under his guidance, I have
travelled around the world, analyzed and unblinded a
historically significant dataset in the field of particle physics, and
participated in one of the largest scientific collaborations in the
history of mankind.  I cannot thank him enough for everything I have
learned, and for all of the amazing scientific opportunities he has
provided.

\par I would like to acknowledge all of the love and support given to
me by my family.  Aunt Carolyn and cousin Gaylon, thank you for all of
the Thanksgiving feasts, and for making me feel at home on the East
Coast.  Little sister, Carrie, thank you for always reminding me to
keep an open heart and mind in all matters in life.  Mom and Dad,
thank for you encouraging me to follow my dreams and giving me every
opportunity to do the things I love.     

\par To the love of my life, Whitney Wegman, you have been the most
incredible source of inspiration and hapiness for me throughout the
three and a half years we have been together at this point.  I cannot
have done this without all of your love and support.  
